Spatial evolution of solar wind discontinuities in the outer heliosphere

### 2024-11-04 article.qmd
fix: update fitting function and improve figure references in article

TODO:
More than ? IDs are identified in the solar wind data from Juno, with ? IDs identified in 5 AU. Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity. After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$. The maximum variance direction is then fitted by a step-like functions to extract the parameters to properly describe the discontinuity (we used logistic function here). Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.

$$
B(t; A, \mu, \sigma, {\mathrm{form=logistic}}) = A \left[1 - \frac{1}{1 + e^{\alpha}} \right]
$${#eq-fit}

where $\alpha = (t - \mu)/{\sigma}$.

@@

where $\mu_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity. For fitting method, the derivative of the magnetic field could be estimated as $d B_m / d t = A / 4 σ$. This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the appendix).

@@

::: {#fig-windDistribution}
![](figures/wind_distribution_time.svg)

@@

::: {#fig-swParameters}
![](figures/sw_paramters_time.svg)

@@

![](figures/ocr/ocr_normalized_by_r.svg)

>>>>

TODO:
More than ? IDs are identified in the solar wind data from Juno, with ? IDs identified in 5 AU. Then for each discontinuity identified, we calculate the distance matrix of the time series sequence (distance between each pair of magnetic field vectors) to determine the leading edge and trailing edge of the discontinuity. After that, we use the minimum or maximum variance analysis (MVA) analysis [@sonnerupMinimumMaximumVariance1998; @sonnerupMagnetopauseStructureAttitude1967] to get the main (most varying) magnetic field component, $B_l$, and medium variation component, $B_m$. The maximum variance direction is then fitted by a hyperbolic tangent functions to extract the parameters to properly describe the discontinuity @eq-fit. Then we combine the magnetic field data and plasma data to obtain the thickness and the current density of the discontinuity.

$$
B_m(t) = B_{m0} \tanh\left(\frac{t - t_0}{\Delta T}\right) + c
$${#eq-fit}

where $B_{m0}$ is the amplitude of the magnetic field change in the maximum variance direction, $t_0$ is the time of discontinuity, $\Delta T$ is the transition time, and $c$ is the offset of the magnetic field change (in the case of an ideal discontinuity with perfect rotational symmetry, $c$ should theoretically be zero. However, in the context of data processing, incorporating $c$ can enhance the fitting accuracy).

@@

where $\mu_0$ is the vacuum permeability and $V_n$ is the normal component of the proton flow velocity. For fitting method, the derivative of the magnetic field could be estimated as $d B_m / d t = B_{m0} / \Delta T$. This estimate is more robust than the direct calculation of the derivative of the magnetic field, because the fitting method is less sensitive to the noise in the data and the time resolution of the data (see discussion in the appendix).

@@

::: {#fig-windDistribution}
![](figures/wind_distribution_time)

@@

::: {#fig-swParameters}
![](figures/wind_sw_paramters)

@@

![](figures/ocr/ocr_normalized_by_r)
